---
title: "TFA_ACT_adhoc"
author: "Marlena Coco"
date: "2024-08-26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# load packages

```{r load libraries}
library(ideadata)
library(tidyverse)
library(here)
library(janitor)
library(DescTools)
library(readr)
library(readxl)
```

# get teacher-student data -----------------

See TFA ad hoc request.Rmd for the code on linking teachers to students.
Pull in the TFA_tch_student_link_file.csv which lists the student numbers needed.

```{r get teacher-student data}
teacher_student <- read.csv(here::here("TFA request", "TFA_tch_student_link_file.csv"))
```


# get ACT data ---------------------------

Because DW has not been fully restored:
Pull in EOY exam-level-data file which already has highest scores calculated
   for ACT including composite and each subject score, and test date.
   It is appropriate to report the highest scores (composite and subject-level) as 
      of EOY because some students may have missed ACT test administrations 
      during the year (like October, April), but an EOY file with documented exam scores
      for each test date throughout a student's career is most comprehensive. 

If DW restored fully and need to pull and clean ACT data, see table:
    # conn_act <- get_table(.table_name = "StudentScores",
    #                       .server_name = "RGVPDSD-DWSRC2",
    #                       .database_name = "SRC_ACT",
    #                       .schema = "ACT") 

```{r get act data}
# determine if import file works or if need to pull and clean. 
exam_level_act <- read.csv(here::here("TFA request", "act-exam-level-data.csv"))
```


# clean act data -------------------
```{r remove most dupes with max test date}
#take one row per student, use the most recent test date 

act_max_date <- exam_level_act %>% 
group_by(Student.Number) %>%
  mutate(max_Test.Date = max(Test.Date)) %>%
  filter(Test.Date == max_Test.Date) %>% 
  mutate(StudentID = Student.Number)

# check duplicates
# duplicates_act_max_date <-act_max_date %>%
#   group_by(StudentID) %>%
#   count() %>% 
#   filter(n>1)

```


# join act data to the student list for TFA

```{r join tfa list and act scores}
# teacher_student %>% 
#   left_join(act_max_date,
#             by = c("StudentID"))

teacher_student_2 <- teacher_student %>% 
  left_join(act_max_date,
            by = c("StudentID"))
```


# clean up teacher-student list by removing students who do not have a max test date.

```{r remove students without act scores}
teacher_student_3 <- teacher_student_2 %>% 
  filter(!is.na(max_Test.Date))
```

```{r}
# check duplicates
# duplicates_teacher_student_3 <- teacher_student_3 %>% 
#   group_by(StudentID) %>%
#   count() %>%
#   filter(n>1)

# duplicates each record 2x
```

# select columns to export

```{r}
teacher_student_4 <- teacher_student_3 %>% 
  
  select(SchoolYear,
         NCES_District_ID,
         StudentID,
         School,
         Grade.Level,
         Student.Number,
         Class.Year,
         Class.Cohort,
         Test.Date,
         Grade.Level.Taken,
         English,
         Mathematics,
         Reading,
         Science,
         Composite,
         Writing,
         STEM,
         ELA,
         Exam.Number,
         Highest.Composite,
         Highest.English,
         Highest.Mathematics,
         Highest.Reading,
         Highest.Science,
         Growth.Previous.Exam,
         Number.Exams.Taken,
         max_Test.Date) %>% 
  distinct()


```


# export to csv and double-check data and request form.

```{r}
write.csv(teacher_student_4, "act-tfa.csv")
```

