---
title: "TFA_ACT_adhoc"
author: "Marlena Coco"
date: "2024-08-26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# load packages

```{r}
library(ideadata)
library(tidyverse)
library(here)
library(janitor)
library(DescTools)
library(readr)
library(readxl)
```

# get teacher-student data -----------------

See TFA ad hoc request.Rmd for the code on linking teachers to students.
Pull in the TFA_tch_student_link_file.csv which lists the student numbers needed.

```{r cars}
teacher_student <- read.csv(here::here("TFA request", "TFA_tch_student_link_file.csv"))
```


# get ACT data ---------------------------
```{r}
# determine if import file works or if need to pull and clean. 
exam-level-act <- read.csv(here::here("TFA request", "act-exam-level-data.csv"))
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
