---
title: "Math-Algebra STAAR request"
author: "Aline Orr"
date: "`r Sys.Date()`"
output: html_document
---

#STAAR math request
This scripts pulls data for Ad Hoc request #1461465846:

1. Student performance on TX State Math Assessments that have achieved "approach, meet, master  standards" for the following subjects: 6th Grade Pre-Algebra, 7th Grade Pre-Algebra, 8th Grade-Algebra I. (Texas: STAAR)
2. Student performance on TX State Math Assessments that have achieved "approach, meet, master standards" for the following subjects: Algebra II, Geometry, Pre-Calculus. (Final Exam-IA's)



```{r setup, include=FALSE}

library(ideadata)
library(tidyverse)
library(janitor)
library(here)
#install.packages("DescTools")
library(DescTools)

STAAR_23_24 <- get_table(.table_name = "STAAR", .database_name = "Dashboard", 
                   .schema = "dbo", .server_name = "RGVPDRA-DASQL") %>%
  filter(TestVersion == "S", 
         ScoreCode == "S",
       #  AdminDate %in% c("0421", "0521")) %>%
         SchoolYear == "2023-2024",
         SubjectCode %in% c("Math", "Algebra I"),
         GradeLevel %in% c("06", "07", "08")) %>%
  select(StudentID,
         LocalStudentID,
         GradeLevel,
         SubjectCode,
         AdminDate,
         ScoreCode,
         ScaleScore,
         Approaches = LevelII,
         Meets = LevelIIFinal,
         Masters = LevelIII) %>%
  mutate(StudentID = as.numeric(StudentID),
         LocalStudentID = as.numeric(LocalStudentID),
         StudentNumber = if_else(LocalStudentID %in% c(0, NA), StudentID, LocalStudentID),
         StudentNumber = as.numeric(StudentNumber)) %>%
  filter(StudentNumber != 0) %>%
  select(-StudentID, -LocalStudentID, -ScoreCode) %>%
  group_by(StudentNumber) %>%
  distinct() %>%
  collect()
  #unique(STAAR)

STAAR_math <- STAAR_23_24 %>%
  group_by(StudentNumber) %>%
  mutate(maxscore = max(ScaleScore))%>%
  filter(ScaleScore == maxscore) %>%
  select(-maxscore, -AdminDate, -ScaleScore)%>%
  distinct()%>%
  ungroup()

pct_levels <- STAAR_math %>%
  mutate(Approaches = as.numeric(Approaches),
         Meets = as.numeric(Meets),
         Masters = as.numeric(Masters),
         Meets1 = case_when((Meets == 1 & Masters == 0) ~ 1,
                            TRUE ~ 0),
         Approaches1 = case_when((Approaches == 1 & Meets == 0) ~ 1,
                               TRUE ~ 0))%>%
  group_by(SubjectCode, GradeLevel) %>%
  mutate(std_n = n(),
         n_apprchs = sum(Approaches1),
         n_meets = sum(Meets1),
         n_mstrs = sum(Masters),
         pct_app = n_apprchs/std_n,
         pct_meet = n_meets/std_n,
         pct_mst = n_mstrs/std_n)

result_table <- pct_levels %>%
  select(SubjectCode, std_n, n_apprchs, n_meets, n_mstrs, pct_app, pct_meet, pct_mst) %>%
  distinct()
write.csv(result_table, "STAAR math & Algebra1 result table.csv")


```

# Pull IDEA internal math results (final exam scores) and summarize as % approaches, % meets, and % masters.

```{r}

iabwa <- get_table(.table_name = "IABWA", 
                     .server_name = "RGVPDSD-DWPRD2", 
                     .schema = "Assessments", 
                     .database_name = "PROD2") %>%
 # collect()
  filter(AcademicYear == "2023-2024",
         AssessmentDate >= "2024-04-20")%>%
  collect()

chk_unique <- iabwa %>%
  select(AssessmentType) %>%
  distinct()

sub_unique <- iabwa %>%
  select(Subject, AssessmentName)%>%
  distinct()

iabwa_mathFE <- iabwa %>%
  filter(AssessmentType == "FE",
         Subject == "Mathematics")

unique_math <- iabwa_mathFE %>%
  select(AssessmentName) %>%
  distinct()

al_pcal_geo_FE <- iabwa_mathFE %>%
  filter(AssessmentName %in% c("LA_MAT_Algebra2_S24_FE",
                               "LA_MAT_Pre-Calculus_S24_FE", 
                               "TX_MAT_Algebra2_S24_FE",
                               "TX_MAT_Pre-Calculus_S24_FE",
                               "TX_MAT_Geometry_S24_FE"))%>%
  select(StudentNumber, AssessmentName, PerfomanceBand)%>%
  group_by(AssessmentName) %>%
  mutate(assess_n = n_distinct(StudentNumber)) %>%
  ungroup()%>%
  group_by(AssessmentName, PerfomanceBand) %>%
  mutate(perf_n = n_distinct(StudentNumber)) %>%
  ungroup()%>%
  filter(PerfomanceBand %in% c("Approaches", "Masters", "Meets"))%>%
  mutate(pband_percent = perf_n/assess_n) %>%
  select(AssessmentName, PerfomanceBand, assess_n, perf_n, pband_percent) %>%
  distinct()

write.csv(al_pcal_geo_FE, "iabwa_math_FE_approaches_meets_masters.csv")

```

